Binary companions of red giant stars with APOGEE: \\ catalog and companions that survive the common envelope

### 2018-02-07 paper/1-catalog/twoface-catalog.tex
References.

Stars typically have companions. Main sequence stars in the solar neighborhood
more often appear in binary or multiple star systems rather than as solitary
stars (\citealt{ragavhan,tokovinin,todo}).
This is likely a generic outcome of star formation: turbulent fragmentation in
collapsing protostellar clouds tends to produce multiplets of stars within
length-scales comparable to their spheres of influence (e.g.,
\citealt{Raskutti:2016}).
Binary and multiple star systems are therefore of great interest in
astrophysics: the population of stars and their companions encodes information
about star formation processes (\citealt{todo}), stellar parameters and
evolution (\citealt{todo}), and the dynamics of multi-body systems
(\citealt{todo}).

>>>>

Stars typically have companions. Main sequence stars in the solar neighborhood
more often appear in binary or multiple star systems rather than as solitary
stars (e.g., \citealt{Duquennoy:1991,Raghavan:2010,Tokovinin:2014}).
This is likely a generic outcome of star formation: For example, turbulent
fragmentation in collapsing protostellar clouds can produce stellar multiplets
within length-scales comparable to their spheres of influence (e.g.,
\citealt{Raskutti:2016}).
Binary and multiple star systems are therefore of great interest in
astrophysics: The population of stars and their companions encodes information
about star formation processes, stellar parameters and evolution, and the
dynamics of multi-body systems (for recent reviews, see
\citealt{Duchene:2013,Moe:2017}).
